Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-09-24 constantRate/ConstCompFuzzExt-reorg.tex
trying to improve table

\begin{table}
\begin{tabular}{l l l c c}
Construction & Security & Source Structure & Error-Tolerance & Alphabet Size\\
\hline
\consref{cons:info theoretic} & Info-theoretic  & Partial block source& $\Theta(\gamma)$ & $\omega(1)$ \\
\consref{cons:sampling} & Reusable Computational & Partial block source& $o(\gamma)$ & $\omega(1)$ \\
\consref{cons:first construction} & Computational & Unguessable block source & $\Theta(\gamma)$ & $n^{\omega(1)}$
\end{tabular}
\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.  Partial blocks sources are defined in \defref{def:partial source} and unguessable block sources are defined in \defref{def:block guessable}.}
\label{tab:upper bounds}
\end{table}

%\begin{table}
%\begin{tabular}{l | l | l | l }
%Construction & Security & Main Feature  & Main Limitations \\
%\hline
%\consref{cons:info theoretic} & Info-theoretic & Exploit distribution & Symbols must add\\
%&&structure & fresh entropy \\\hline
%\consref{cons:sampling} & Computational  & Reusability & Sub-constant fraction \\
%&& & error tolerance\\\hline
%\consref{cons:first construction} & Computational & Allows correlated & Super-polynomial \\
%& &  symbols & size symbols
%\end{tabular}
%\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
%\label{tab:upper bounds}
%\end{table}

@@

An additional desirable feature of fuzzy extractors is reusability~\cite{Boyen2004}. Inuitively, it is the ability to support multiple independent enrollments of the same value, allowing users to reuse the same biometric or PUF, for example, with multiple noncommunicating providers. More precisely, the algorithm $\gen$ may be run multiple times on correlated readings $w_1,..., w_q$ of a given source. Each time, $\gen$ will produce a different pair of values $(r_1, p_1),..., (r_q, p_q)$. Security for each extracted string $r_i$ should hold even in the presence of all the helper strings $p_1, \dots, p_q$ (even though the reproduction procedure $\rep$ at the $i$th provider obtains only a single $w'_i$ close to $w_i$ and uses a single helper string $p_i$). Because the multiple providers may not trust each other, a stronger security feature (which we satisfy) ensures that each $r_i$ is secure even when all $r_j$ for $j\neq i$ are also given to the adversary.

@@

\begin{definition}[Reusable Fuzzy Extractors]
\label{def:outsider fuzz ext}
Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
\begin{itemize}%[leftmargin=-.6in]
\item \textbf{Sampling} The challenger samples $w_1\leftarrow W_1$.
\item \textbf{Perturbation} For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.  Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.% The output $p_i$ is provided to $\mathcal{A}$, who selects $\delta_i:\mathcal{M}\rightarrow \mathcal{M}$.  The challenger sets $w_{i+1} = \delta_i(w_1)$.
\item \textbf{Distinguishing} The advantage of $D$ is
\begin{align*}
\text{Adv}(D)&\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1]\\ &- \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
\end{align*}
where $u$ is a uniformly random string.
\end{itemize}
$(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D\in\mathcal{D}_{s_{sec}}$ the advantage is at most $\epsilon_{sec}$.
\end{definition}

@@

\subsection{More errors than entropy?}
In this section, we show when \consref{cons:sampling} supports partial block sources with more errors than entropy.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) < t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.  We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.  However, \consref{cons:sampling} is reusability for an arbitrary size alphabet.

@@

The goal of a reusable fuzzy extractor is to allow enrollment of a source across multiple services.  A service $i$ sees an reading of the source $w_i$.
Boyen considers two versions of reusable fuzzy extractors, first where the adversary sees $p_1,..., p_q$~(outsider security~\cite[Definition 6]{Boyen2004}) and tries to learn about the values $w_1,..., w_q$ or the keys $r_1,..., r_q$.  Second, where the adversary controls some subset of the servers and can key generation on arbitrary $p_i'$~(insider security~\cite[Definition 7]{Boyen2004}).   This allows the adversary to learn a subset of keys $r_i$~(by performing key generation on the valid $p_i$).  This definition makes sense when servers are compromised~(after enrollment) and act maliciously.

Boyen constructs a outsider reusable cryptographic fuzzy extractor for unbounded $q$ when the correlation between readings is limited to a transitive isometric permutation groups. Boyen transforms this construction to insider security using random oracles. %In both constructions, the correlation between  $w_1,..., w_q$ is limited to a transitive isometric permutation group.

Insider security strengthens outsider security in two ways.  First, it allows the adversary to see some subset of keys, second it allows the adversary to perform regeneration on arbitrary $p_i$.  This mixes two properties of a fuzzy extractor:  reusability and robustness~\cite{dkrs2006}.  Robust fuzzy extractors provide security against modified $p$.  
In this work, we show reusability when some $r_i$ are observed but do not handle the issue of robustness.  That is, we assume passive servers.  Our definition lies between outsider and insider security.

>>>>

\begin{table}
{ \centering
\begin{tabular}{l l l l l}
 & Security & Source Structure & Error-Tolerance & Alphabet Size\\
\hline
Cons. \ref{cons:info theoretic} & Info-theoretic  & Most symbols  & Constant fraction & Super constant \\
& & contribute entropy & &\\\hline
Cons. \ref{cons:sampling} & Reusable & Most symbols & Sub constant fraction & Super constant \\
& Computational & contribute entropy & &\\\hline
Cons. \ref{cons:first construction} & Computational & Symbols correlated  & Constant fraction & Super\\
& & but hard to guess && polynomial
\end{tabular}
}%end centering
\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
\label{tab:upper bounds}
\end{table}

\bnote{can't get this table to center don't know why}
%\begin{table}
%\begin{tabular}{l | l | l | l }
%Construction & Security & Main Feature  & Main Limitations \\
%\hline
%\consref{cons:info theoretic} & Info-theoretic & Exploit distribution & Symbols must add\\
%&&structure & fresh entropy \\\hline
%\consref{cons:sampling} & Computational  & Reusability & Sub-constant fraction \\
%&& & error tolerance\\\hline
%\consref{cons:first construction} & Computational & Allows correlated & Super-polynomial \\
%& &  symbols & size symbols
%\end{tabular}
%\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
%\label{tab:upper bounds}
%\end{table}

@@

An additional desirable feature of fuzzy extractors is reusability~\cite{Boyen2004}. Inuitively, it is the ability to support multiple independent enrollments of the same value, allowing users to reuse the same biometric or PUF, for example, with multiple noncommunicating providers. More precisely, the algorithm $\gen$ may be run multiple times on correlated readings $w_1,..., w_q$ of a given source. Each time, $\gen$ will produce a different pair of values $(r_1, p_1),..., (r_q, p_q)$. Security for each extracted string $r_i$ should hold even in the presence of all the helper strings $p_1, \dots, p_q$ (the reproduction procedure $\rep$ at the $i$th provider still obtains only a single $w'_i$ close to $w_i$ and uses a single helper string $p_i$). Because the multiple providers may not trust each other, a stronger security feature (which we satisfy) ensures that each $r_i$ is secure even when all $r_j$ for $j\neq i$ are also given to the adversary.

@@

\begin{definition}[Reusable Fuzzy Extractors]
\label{def:outsider fuzz ext}
Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
\begin{itemize}%[leftmargin=-.6in]
\item \textbf{Sampling} The challenger samples $w_1\leftarrow W_1$.
\item \textbf{Perturbation} For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.  Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.\bnote{should we allow keys to the perturbation adversary?}
\item \textbf{Distinguishing} The advantage of $D$ is
\begin{align*}
\text{Adv}(D)&\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1]\\ &- \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
\end{align*}
where $u$ is a uniformly random string.
\end{itemize}
$(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D\in\mathcal{D}_{s_{sec}}$ the advantage is at most $\epsilon_{sec}$.
\end{definition}

@@

\subsection{More errors than entropy?}
In this section, we show when \consref{cons:sampling} supports partial block sources with more errors than entropy.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) < t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.

\textbf{Note:} \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.  However, \consref{cons:sampling} is reusability for an arbitrary size alphabet.

@@

The goal of a reusable fuzzy extractor is to allow enrollment of a source across multiple services.  A service $i$ sees an reading of the source $w_i$.
Boyen considers two versions of reusable fuzzy extractors, first where the adversary sees $p_1,..., p_q$~(outsider security~\cite[Definition 6]{Boyen2004}) and tries to learn about the values $w_1,..., w_q$ or the keys $r_1,..., r_q$.  Second, where the adversary controls some subset of the servers and can key generation on arbitrary $p_i'$~(insider security~\cite[Definition 7]{Boyen2004}).   This allows the adversary to learn a subset of keys $r_i$~(by performing key generation on the valid $p_i$).  This definition makes sense when servers are compromised~(after enrollment) and act maliciously.  In both definitions, the adversary creates a perturbation function $_i$ after seeing $p_1,..., p_{i-1}$~(and generated keys for outsider security) and the challenger generates $w_i = f_i(w_1)$.  The definition is parameterized by the class of allowed perturbation functions.

Boyen constructs a outsider reusable cryptographic fuzzy extractor for unbounded $q$ when the perturbation family is a transitive isometric permutation groups. Boyen transforms this construction to insider security using random oracles. %In both constructions, the correlation between  $w_1,..., w_q$ is limited to a transitive isometric permutation group.

Insider security strengthens outsider security in two ways.  First, it allows the adversary to see some subset of keys, second it allows the adversary to perform key generation on arbitrary $p_i$.  This mixes two properties of a fuzzy extractor:  reusability and robustness~\cite{dkrs2006}.  Robust fuzzy extractors provide security against modified $p$.  
In this work, we show reusability when $r_i$ are observed but do not handle the issue of robustness.  That is, we assume keys may be exposed but servers keep honest state.  Our definition lies between outsider and insider security.
